\chapter{Global Governance and the Open HAWRA Foundation}

\section{The Need for International Regulation}
The deployment of HAWRA at a planetary scale requires a new framework for international cooperation. We must avoid a "Biotic Arms Race" and ensure that the benefits of metabiotic computing are shared equitably.

\subsection{The Universal Declaration of Metabiotic Rights}
We call for the adoption of the Universal Declaration of Metabiotic Rights by the United Nations, establishing the legal status of HAWRA nodes and the ethical boundaries of their use.

\section{The Open HAWRA Foundation (OHF)}
To prevent the monopolization of HAWRA technology, we have established the Open HAWRA Foundation (OHF). The OHF manages the open-source development of the BioOS, ARBOL, and the pHAWRA plasmid blueprints.

\subsection{The "Planetary License"}
All HAWRA-related technologies are released under the OHF "Planetary License," which requires that any commercial use of the technology must contribute a percentage of its profits to a global "Biosphere Restoration Fund."

\section{Global Deployment Zones (GDZs)}
We propose the creation of Global Deployment Zones (GDZs), where HAWRA technology can be tested and deployed under strict international oversight. These zones will serve as "Living Labs" for studying the long-term ecological impact of metabiotic systems.

\subsection{Monitoring and Verification}
The OHF will maintain a global network of "Audit Nodes" that monitor the health and genomic integrity of HAWRA forests in real-time, ensuring that no GDZ exceeds its metabolic or ecological carrying capacity.

\section{The Role of the Individual: Citizen-Stewards}
HAWRA is not just for corporations and governments. We envision a future where individuals can "host" a HAWRA node in their own gardens or balconies, contributing to the global mesh and earning CCT rewards.

\subsection{The "HAWRA-at-Home" Program}
The OHF provides low-cost "Starter Kits" (including a pre-transformed \textit{Arabidopsis} plant and a mini-BioOS controller) to encourage public participation in the metabiotic revolution.
